---
title: "Chapter_Crue: Tidy data and prepare datasets"
author: "Aline Carvalho"
date: "09/03/2021"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

# Changes in MP pollutiong during flood are modulated by urbanization

```{r libraries}
library(readxl)
library(tidyverse)
library(baseline)
```

## Pre-objective: tidydata

## October 2018 Crue analysis

#### Data synthesis: MP concentration 

```{r read_samplingA}
#setwd("C:/Users/postdoc/OneDrive/2. Doutorado/99. Redaction_Articles_these/Z. These/1.RMarkdown_chapters")
lmp_samplingA <- read_xlsx("rawdata/data_PLASTIGAR_25092020_A.xlsx")

lmp_samplingA <- lmp_samplingA %>%
  filter(Sampling_gear == "FILET") %>%
  filter(Mesh_size == "500") %>%
  filter(Season == "A") %>%
  mutate(Volume = as.numeric(Volume)) %>%
  mutate(nb_particles = as.numeric(nb_particles))%>%
  mutate(particles_m3 = nb_particles / Volume)%>%
  mutate(NTU = as.numeric(NTU)) %>%
  mutate(`Debit (m3/s)` = as.numeric(`Debit (m3/s)`))%>%
  mutate(Site=ifelse(Code_station == 6, "MUG",
                     ifelse(Code_station == 11, "GSG", Code_station)))%>%
  mutate(particles_m3_cor = particles_m3 * 0.7848982) # correct for the microplastic rate based on Flood B

lmp_samplingA_crue <- lmp_samplingA %>%
  filter(Code_station == 6 | Code_station == 11) 
```

```{r write_samplinA}
write.csv(lmp_samplingA_crue, "data/lmp_samplingA_crue.csv")
```

## May/June 2019 Crue analysis

### Data synthesis: Particles

```{r read_lmpwater}
lmp_water <- read_xlsx("rawdata/LMP_water_loupe_V11_shape.xlsx")
names(lmp_water)
lmp_particles <- lmp_water %>%
  filter(Season!= "A" & Season!= "B" & Season != "E") %>%
  filter(Sampling_gear=="FILET")%>%
  filter(Site==6 | Site==8 | Site==11)

length(unique(lmp_particles$Sample_ID))
unique(lmp_particles$Color)

lmp_particles <- lmp_particles %>%
  mutate(Color = as.character(Color)) %>%
  mutate(Color = replace(Color, Color == "Pink", "Red"))%>%
  mutate(Color = replace(Color, Color == "blue", "Blue"))%>%
  mutate(Color = replace(Color, Color == "black", "Black"))%>%
  mutate(Color = replace(Color, Color == "green", "Green"))%>%
  mutate(Color = replace(Color, Color == "white", "White"))%>%
  mutate(Color = replace(Color, Color == "brown", "Red"))%>%
  mutate(Color = replace(Color, Color == "red", "Red"))%>%
  mutate(Color = replace(Color, Color == "grey", "Grey"))%>%
  mutate(Color = replace(Color, Color == "Purple", "Red"))%>%
  mutate(Color = replace(Color, Color == "orange", "Red"))%>%
  mutate(Color = replace(Color, Color == "purple", "Red"))%>%
  mutate(Color = replace(Color, Color == "pink", "Red"))%>%
  mutate(Color = replace(Color, Color == "transparent", "White")) %>%
  mutate(Color = replace(Color, Color == "Brown", "Red"))%>%
  mutate(Color = replace(Color, Color == "Transparent", "White"))

unique(lmp_particles$IR_ID)

lmp_particles <- lmp_particles %>%
  mutate(IR_ID = as.character(IR_ID)) %>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "CELLULOSE", "non-plastic"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "STEARATE DE CALCIUM", "Additive"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "calcium stearate", "Additive"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "à determiner", "NA"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "à déterminer", "NA"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "RUBBER (SBR)" , "Polydienes"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "ADDITIVES", "Additive"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "OLEFIN", "Additive"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "poly(éthylène-propylène )", "PP"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "MINERAL", "non-plastic"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "ASPHALT A-67", "Asphalt"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "RUBBER (EPR)", "Polydienes"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "RUBBER", "Polydienes"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "Parafin", "Additive"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "glicerol trioleate", "Additive"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "weston 619", "Additive"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "asphalt", "Asphalt"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "PBS", "Additive"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "Aragonite", "non-plastic"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "pp", "PP"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "PSEB", "Polydienes"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "poly butylene terephthalate", "Polyester"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "POLYESTER", "Polyester"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "SEB", "Polydienes"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "kodak epolene", "PE"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "Styrene/ACN copolymer", "PS"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "AC 175", "Additive"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "NYLON", "Polyamide"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "PDMS", "Polisiloxane"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "polydimethylsiloxane", "Polisiloxane"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "Styrene/ACN copolymer", "PS"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "THERMOPLASTIQUES", "Polydienes"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "poly(styrene décaméthylène)", "Polydienes"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "POLYURETHANE", "PU")) %>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "AC 715", "Additive"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "THERMOPLASTIQUE", "Polydienes"))%>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "ACRYLATE", "Polyacrylate")) %>%
  mutate(IR_ID = replace(IR_ID, IR_ID == "polyacrylate", "Polyacrylate"))

names(lmp_particles)

lmp_particles <- lmp_particles %>%
    mutate(Length_mm = as.numeric(Length_mm)) %>%
    filter(IR_ID != "NA") %>%
   filter(IR_ID != "NS")%>%
  filter(IR_ID != "à determiner") %>%
   filter(IR_ID != "non-plastic") %>%
  filter(Length_mm >= 0.7) %>%
  filter (Length_mm <= 5) %>%
  mutate(Area = as.numeric(Area)) %>%
  mutate(Perim = as.numeric(Perim)) %>%
  mutate(Weight_mg = as.numeric(Weight_mg))

lmp_particles<-lmp_particles%>%mutate_if(is.character, ~replace(., is.na(.), "NA"))

length(unique(lmp_particles$Sample_ID))
```

```{r tidydata_lmpwater}
# Create ID_particle
lmp_particles <- unite (lmp_particles,"ID_particle", Box_ID:Box_Position,sep="-") # without BOX_ID

#Standarlize Sample_ID
names(lmp_particles)

lmp_particles <- lmp_particles[,c(1,2,4,5,3,6,7,8,10,11,15,13,19,20,21,22)]
lmp_particles <- unite (lmp_particles, "Sample_ID", Site : Replica : Season , sep="-", remove = FALSE)
length(unique(lmp_particles$Sample_ID))
```

### Data synthesis: Sampling

```{r read_dataPLASTIGAR}
lmp_sampling <- read_xlsx("rawdata/data_PLASTIGAR_25092020.xlsx")

names(lmp_sampling)

lmp_sampling <- lmp_sampling[,c(1,6,7,8,9,15,18,25)]

lmp_sampling <- lmp_sampling %>%
  filter(Season== "C" | Season == "C1" | Season == "C2" | Season == "C3" | Season =="C4" | Season == "D") %>%
  filter(Sampling_gear=="FILET")%>%
  filter(Code_station==6 | Code_station==8 | Code_station==11)%>%
  filter(Mesh_size=="500")%>%
  filter(Replicate<=3)

lmp_sampling <- lmp_sampling[,c(1,4,5,6,7,8)]

lmp_sampling <- unite (lmp_sampling, "Sample_ID", Code_station : Replicate : Season , sep="-", remove = FALSE)

names(lmp_sampling)

lmp_sampling <- lmp_sampling %>%
  mutate(Code_station = replace(Code_station, Code_station == '6', "MUG")) %>%
  mutate(Code_station = replace(Code_station, Code_station == '8', "LAU")) %>%
  mutate(Code_station = replace(Code_station, Code_station == '11', "GSG")) %>% 
  mutate(river=ifelse(Code_station=="GSG", "Garonne",
                      ifelse(Code_station=="MUG", "Garonne","Tributary")))

length(unique(lmp_sampling$Sample_ID))
```

### MP concentration (number & mass): Data synthesis

```{r tidydata_lmpcruequanti}
names(lmp_particles)

lmp_particlesv2 <- lmp_particles %>%
  group_by(Site,Sample_ID,Replica,Season)%>%
  summarise(Nb_plastic = n(), mass_plastic_mg=sum(Weight_mg, na.rm = TRUE))

#Join field data with quantity of plastic per sample data => lmp_crue
lmp_crue <- right_join(lmp_particlesv2, lmp_sampling, by=c("Sample_ID"), keep = FALSE, copy = FALSE)

names(lmp_crue)

lmp_crue <- lmp_crue %>%
  mutate(Volume=as.numeric(Volume))%>%
  mutate(Conc_nb_plastic_m3 = Nb_plastic / Volume, 
         Conc_mass_plastic_mg_m3 = mass_plastic_mg / Volume)%>%
  mutate_if(is.numeric, ~replace(., is.na(.), 0))%>%
  mutate(Site=as.character(Site))%>%
  mutate(Replica=as.character(Replica))%>%
  mutate(Site=ifelse(Sample_ID=="6-1-C1", "6", Site))%>%
  mutate(Site=ifelse(Sample_ID=="6-1-C2", "6", Site))%>%
  mutate(Site=ifelse(Sample_ID=="6-1-C4", "6", Site))%>%
  mutate(Site=ifelse(Sample_ID=="6-2-C1", "6", Site))%>%
  mutate(Site=ifelse(Sample_ID=="6-3-C2", "6", Site))%>%
  mutate(Site=ifelse(Sample_ID=="11-2-D", "11", Site))%>%
  mutate(Replica=ifelse(Sample_ID=="6-1-C1", "1", Replica))%>%
  mutate(Replica=ifelse(Sample_ID=="6-1-C2", "1", Replica))%>%
  mutate(Replica=ifelse(Sample_ID=="6-1-C4", "1", Replica))%>%
  mutate(Replica=ifelse(Sample_ID=="6-2-C1", "2", Replica))%>%
  mutate(Replica=ifelse(Sample_ID=="6-3-C2", "3", Replica))%>%
  mutate(Replica=ifelse(Sample_ID=="11-2-D", "2", Replica)) %>%
  mutate(`Debit (m3/s)` = as.numeric(`Debit (m3/s)`))%>%
  mutate(NTU=as.numeric(NTU)) 

lmp_crue <- lmp_crue %>%
   mutate(Season.y = replace(Season.y, Season.y == "C", "B1")) %>%
  mutate(Season.y = replace(Season.y, Season.y == "C1", "B2")) %>%
  mutate(Season.y = replace(Season.y, Season.y == "C2", "B3")) %>%
  mutate(Season.y = replace(Season.y, Season.y == "C3", "B4")) %>%
  mutate(Season.y = replace(Season.y, Season.y == "C4", "B5")) %>%
  mutate(Season.y = replace(Season.y, Season.y == "D", "B6")) %>% 
  mutate(Flood = ifelse(Season.y == "B1", 'Without', 
                        ifelse(Season.y == "B2", 'Without',
                               ifelse(Season.y == "B3", 'Without', 
                                      ifelse(Season.y == "B4", 'With',
                                             ifelse(Season.y == "B5", 'Without',
                                                    ifelse(Season.y == "B6", 'Without', Season.y)))))))

lmp_crue <- lmp_crue %>%
  mutate(Code_station = replace(Code_station, Code_station == '6', "MUG")) %>%
  mutate(Code_station = replace(Code_station, Code_station == '8', "LAU")) %>%
  mutate(Code_station = replace(Code_station, Code_station == '11', "GSG")) %>% 
  mutate(river=ifelse(Code_station=="GSG", "Garonne",
                      ifelse(Code_station=="MUG", "Garonne","Tributary")))

lmp_crue$Code_station <- factor(lmp_crue$Code_station , levels=c("MUG","GSG","LAU"))

names(lmp_crue)
lmp_crue %>%
  group_by(Code_station) %>%
  summarise(meannb = mean(Conc_nb_plastic_m3), meanmass = mean(Conc_mass_plastic_mg_m3))
```

```{r write_lmpcrue}
write.csv(lmp_crue, "rawdata/lmp_crue.csv")
```

### MP characteristics: Shape descriptors

1) Corey Shape Factor (CSF) = H/((LW)^1/2)

2) Sphericity = (WH/(L^2))^1/3

3) Shape legend (equivalent width):

1 = line (W = H)
2 = film (W = 0.08)
3 = fragment (W = 0.33)
4 = pellet (W = L/2)
5 = bead/sphere (W = (L+H/2))

```{r tidydata_lmpparticles}
names(lmp_particles)

lmp_particles <- lmp_particles %>%
  mutate(Largeur_mm = as.numeric(Largeur_mm)) %>%
  mutate(L = Length_mm) %>%
  mutate(H = Largeur_mm) %>%
  mutate(W = ifelse(Shape == "1", H, ifelse
                    (Shape == "2", 0.08, ifelse
                      (Shape == "3", 0.33, ifelse
                        (Shape == "4", L/2, ifelse
                          (Shape == "5", ((L+H)/2), Shape)))))) %>%
  mutate(L = as.numeric(L)) %>%
  mutate(H = as.numeric(H)) %>%
  mutate(W = as.numeric(W)) %>%
  mutate(CSF = H/((L*W)^(1/2))) %>% # CSF
  mutate(Spher = ((W*H/(L^2))^(1/3))) %>% # Sphericity
  mutate(Shapes = ifelse(Shape == "1", "line", ifelse
                          (Shape == "2", "film", ifelse
                            (Shape == "3", "fragment", ifelse
                              (Shape == "4", "pellet", ifelse
                                (Shape == "5", "sphere", Shape)
                            )))))

lmp_particles$Shapes <- factor(lmp_particles$Shapes, levels=c("line", "film", "fragment", "pellet", "sphere"))

ggplot(lmp_particles, aes(x = Shapes, y = Spher, fill = Shapes))+
  geom_boxplot(alpha=0.5) +
  ylab("Sphericity") +
  ggtitle("MP sphericity", subtitle = "Among shapes categories (n=1580)")+
  xlab("Shape") +
  scale_fill_brewer(palette = "RdBu") +
  theme_classic(base_size = 18) 
```

### MP characteristics: New categories

```{r tidydata_lmpcruequal}
lmp_crue_qual <- right_join(lmp_particles, lmp_sampling, by=c("Sample_ID"), keep = FALSE, copy = FALSE)

lmp_crue_qual <- lmp_crue_qual %>%
  mutate(Volume=as.numeric(Volume))%>%
  mutate_if(is.numeric, ~replace(., is.na(.), 0))%>%
  mutate(Site=as.character(Site))%>%
  mutate(Replica=as.character(Replica))%>%
  mutate(Site=ifelse(Sample_ID=="6-1-C1", "6", Site))%>%
  mutate(Site=ifelse(Sample_ID=="6-1-C2", "6", Site))%>%
  mutate(Site=ifelse(Sample_ID=="6-1-C4", "6", Site))%>%
  mutate(Site=ifelse(Sample_ID=="6-2-C1", "6", Site))%>%
  mutate(Site=ifelse(Sample_ID=="6-3-C2", "6", Site))%>%
  mutate(Site=ifelse(Sample_ID=="11-2-D", "11", Site))%>%
  mutate(Replica=ifelse(Sample_ID=="6-1-C1", "1", Replica))%>%
  mutate(Replica=ifelse(Sample_ID=="6-1-C2", "1", Replica))%>%
  mutate(Replica=ifelse(Sample_ID=="6-1-C4", "1", Replica))%>%
  mutate(Replica=ifelse(Sample_ID=="6-2-C1", "2", Replica))%>%
  mutate(Replica=ifelse(Sample_ID=="6-3-C2", "3", Replica))%>%
  mutate(Replica=ifelse(Sample_ID=="11-2-D", "2", Replica)) %>%
  mutate(`Debit (m3/s)` = as.numeric(`Debit (m3/s)`))%>%
  mutate(NTU=as.numeric(NTU)) %>%
  mutate(Site = replace(Site, Site == '6', "MUG")) %>%
  mutate(Site = replace(Site, Site == '8', "LAU")) %>%
  mutate(Site = replace(Site, Site == '11', "GSG")) %>% 
  mutate(river=ifelse(Site=="GSG", "Garonne",
                      ifelse(Site=="MUG", "Garonne","Tributary"))) %>%
  filter(Nb_particules > 0) %>%
  mutate(IR_ID_bis= ifelse(IR_ID=="Additive",'others', IR_ID )) %>%
  mutate(IR_ID_bis= ifelse(IR_ID_bis=="Polyester",'others', IR_ID_bis )) %>%
  mutate(IR_ID_bis= ifelse(IR_ID_bis=="PU",'others', IR_ID_bis )) %>%
  mutate(IR_ID_bis= ifelse(IR_ID_bis=="Polydienes",'others', IR_ID_bis )) %>%
  mutate(IR_ID_bis= ifelse(IR_ID_bis=="Polyacrylate",'others', IR_ID_bis )) %>%
  mutate(IR_ID_bis= ifelse(IR_ID_bis=="Asphalt",'others', IR_ID_bis )) %>%
  mutate(IR_ID_bis= ifelse(IR_ID_bis=="EVA",'others', IR_ID_bis )) %>%
  mutate(IR_ID_bis= ifelse(IR_ID_bis=="Polisiloxane",'others', IR_ID_bis )) %>%
  mutate(Flood = ifelse(Season.y == "C", 'Without', 
                        ifelse(Season.y == "C1", 'Without',
                               ifelse(Season.y == "C2", 'Without', 
                                      ifelse(Season.y == "C3", 'With',
                                             ifelse(Season.y == "C4", 'Without',
                                                    ifelse(Season.y == "D", 'Without', Season.y)))))))%>%
  mutate(Sampling_event = ifelse(Season.y == "C", 'B1', 
                        ifelse(Season.y == "C1", 'B2',
                               ifelse(Season.y == "C2", 'B3', 
                                      ifelse(Season.y == "C3", 'B4',
                                             ifelse(Season.y == "C4", 'B5',
                                                    ifelse(Season.y == "D", 'B6', Season.y)))))))

# due to low quantity of particles in some flood days (d2 and d1 for MUG), a new group was created: before, during and after flood
  
lmp_crue_qual$Site <- factor(lmp_crue_qual$Site , levels=c("MUG","GSG","LAU"))

lmp_crue_qual$IR_ID_bis <- factor(lmp_crue_qual$IR_ID_bis,levels=c("PE", "PS", "PP", "others"))

lmp_crue_qual$Flood <- factor(lmp_crue_qual$Flood, levels=c("Without","With"))
```

```{r write_lmpcruequal}
write.csv(lmp_crue_qual, "rawdata/lmp_crue_qual.csv")
```

### MP ATR-FTIR: 

#### Function stdfilename & readIR

```{r stdfilenamefunc}
std_filename = function(){
  file_list = list.files()
  for(file in file_list){
    name = file %>% str_replace_all("@@", "") %>%
    str_replace_all(".CSV", "") %>%
    str_replace_all("_", "") %>%
    str_replace_all("-", "") %>%
    str_replace_all("[A]", "-A") %>%
    str_replace_all("[B]", "-B") %>%
    str_replace_all("[C]", "-C") %>%
    str_replace_all("[D]", "-D") %>%
    str_replace_all("[E]", "-E") %>%
    str_replace_all("[F]", "-F") %>%
    str_replace_all("[G]", "-G") %>%
    str_replace_all("[H]", "-H")
    temp_dataset = read_csv(file, col_names = c("wl", name))
    temp_dataset = temp_dataset %>%
      drop_na() %>%
      mutate(wl=as.numeric(wl)) %>% 
      mutate(wl=round(wl, digits=2))
    if(exists("dataset")){
      dataset <- inner_join(dataset, temp_dataset, by = "wl")
    } else{
      dataset = temp_dataset
    }
      }
  dataset %>%
    drop_na()
  return(dataset)
}
  
```

```{r readirfunc}
readir = function(){
  file_list <- list.files()
  #dataset = tibble(wl=1.2)
  for(file in file_list){
    name = file
    temp_dataset = read_csv(file, col_names = c("wl", name))
    temp_dataset = temp_dataset %>%
      drop_na() %>%
      mutate(wl=as.numeric(wl)) %>% 
      mutate(wl=round(wl, digits=2))
    if(exists("dataset")){
      dataset <- inner_join(dataset, temp_dataset, by = "wl")
    } else{
      dataset = temp_dataset
    }
    #dataset <- right_join(dataset, temp_dataset, by = "wl")
  }
  dataset %>%
    drop_na()
  return(dataset)
}
```

#### Organize dataset

```{r read_specpe}
#setwd("rawdata/PE")
#pe_db = std_filename()
```

```{r write_specpe}
#setwd("")
#write_csv(pe_db, file="rawdata/pe_db.csv")
pe_db=read_csv(file="data/pe_db.csv")
```

```{r dataframes_specs}
pe_df = as.data.frame(t(pe_db)) # 541 obs of 7400 variables
colnames(pe_df) <- pe_df[1,] # change col names by copying the first row
pe_df = pe_df[-1,] # delete the first row

wl <- colnames(pe_df)
```

```{r}
lmp_crue_qual = read.csv("rawdata/lmp_crue_qual.csv")
lmp_crue_qual_gar <- lmp_crue_qual %>%
  filter(river=="Garonne")
```

```{r innerjoinspecGAR}
pe_df = pe_df %>% mutate(ID_particle=rownames(pe_df))
pe_gar = inner_join (lmp_crue_qual_gar, pe_df, by="ID_particle") # 72 obs of 7432 var
pe_gar_spec = pe_gar[,-(1:32)]
pe_gar_qual = pe_gar[,(1:32)]
```

#### Spectra pre-treatment

##### PE

###### Garonne

```{r plot_spec}
names(pe_gar)
pe_gar_gsg <- pe_gar %>%
  filter(Site == "GSG")
pe_gar_gsg_mat <- as.matrix(pe_gar_gsg[,33:7432])
g = matplot(wl, t(pe_gar_gsg_mat), type="l", xlab="wavenumber (cm-1)", ylab="absorbance")

```

```{r pretreat_peGAR}
pe_gar_mat <- as.matrix(pe_gar_spec)
# 72 obs of 7400 variables
matplot(wl, t(pe_gar_mat), type="l", xlab="wavenumber", ylab="absorbance")

# BASELINE CORRECTION (by Kedzierski et al, 2019; Liland 2015)

t = baseline(pe_gar_mat, lambda=4, hwi=50, it=10, int=740, method='fillPeaks')
#x = t@spectra # original
#u = t@baseline # baseline to be subtracted
pe_gar_mat_base = as.matrix(t@corrected) # corrected

matplot(wl, t(pe_gar_mat_base), type="l", xlab="wavenumber", ylab="absorbance")

# Tests
#x = pe_gar_mat[1,]
#y = scale(pe_gar_mat[1:10,], scale=FALSE, center = TRUE)
#z = scale(t(pe_gar_mat[1:5,]), scale=FALSE, center = TRUE)

#matplot(wl, x, type="l", xlab="wavenumber", ylab="absorbance")

# NORMALIZATION BY THE SUM (by Jung et al, 2018)
v1 <- colSums(t(pe_gar_mat_base))
pe_gar_mat_base_sum_norm <- pe_gar_mat_base / v1
matplot(wl, t(pe_gar_mat_base_sum_norm), type="l", xlab="wavenumber", ylab="absorbance")

# t <- colSums(t(pe_gar_mat_base_sum_norm)) #test

#pe_gar_mat_base_norm <- scale(t(pe_gar_mat_base), scale=FALSE, center = TRUE)
# so then each columns represents a spectra
#pe_gar_mat_base_norm  <- t(pe_gar_mat_base_norm) #return to the matrix where each row is a spectra to perform PCA
#matplot(wl, t(pe_gar_mat_base_norm), type="l", xlab="wavenumber", ylab="absorbance")
# one spectra outlier -> remove spectra "6" 
# (equivalent = 20-A1)

pe_gar_mat_base_sum_norm <- pe_gar_mat_base_sum_norm [-6,]
matplot(wl, t(pe_gar_mat_base_sum_norm), type="l", xlab="wavenumber", ylab="absorbance")

pe_gar_qual2 <- pe_gar_qual %>%
  filter(ID_particle != "20-A1" ) 

pe_gar_qual2 = pe_gar_qual2 %>%
  select(c(1,8,30,31,32))

pe_gar_qual_spec <- bind_cols(pe_gar_qual2, as.data.frame(pe_gar_mat_base_sum_norm))
```


```{r write_pretreat_peGAR}
write_csv(pe_gar_qual_spec,"data/pe_gar_qual_spec.csv")
```

1.1) Test with select wavenuber:
1) Range 1 = 800 - 1300
2) Range 2 = 1650 - 2100
3) Range 3 = 3100 - 3700

```{r selectedwlPE}
t=as.data.frame(t(pe_gar_mat_base_sum_norm))
t$wl = rownames(t)

pe_mat_selectwl <- t %>%
  filter( wl > 800 & wl < 1300 | wl > 1650 & wl < 2100 | wl > 3100 & wl < 3700 )

pe_mat_selectwl = t(pe_mat_selectwl[,-72]) # 1229 obs of 72 variables

pe_gar_qual_spec_selectwl <- bind_cols(pe_gar_qual2, as.data.frame(pe_mat_selectwl))
```


```{r write_selectedwlPE}
write_csv(pe_gar_qual_spec_selectwl,"data/pe_gar_qual_spec_selectwl.csv")

#pe_gar_selectwl = inner_join (pe_gar_qual_gar2, pe_df_selectwl, by="ID_particle")
#pe_gar_spec_selectwl = pe_gar_selectwl[,-(1:32)]
#pe_gar_qual_selectwl = pe_gar_selectwl[,(1:32)]

#wl <- colnames(pe_df_selectwl)
```

